BivData Setup

### 2020-02-13 src/BivData_Setup.Rmd
cleaning up more

@@

@@

The below cell level table is used for making the **long.biv.dataset**, (any others?)

@@

# Long BivData Set

@@

  the.Q4 <-cell.level.BivData_table$Qar.4[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]
   the.Q3 <-cell.level.BivData_table$Qar.3[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]
  the.Q2 <-cell.level.BivData_table$Qar.2[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]

@@

#3.mark which bivalents are above the threshold
#WHY DOESN"T THIS WORK?

@@

>>>>

  6. Long Biv Dataset and short biv dataset

@@

new.Curate.FULL.org$Obj.ID <- paste(new.Curate.FULL.org$fileName, new.Curate.FULL.org$boxNumber, sep = "_")

@@

The below cell level table is used for making the **long.biv.dataset** and short, (any others?)

@@

# Long and Short BivData Set

@@

  the.Q4 <- cell.level.BivData_table$Qar.4[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]

  the.Q3 <-cell.level.BivData_table$Qar.3[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]

  the.Q2 <-cell.level.BivData_table$Qar.2[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]

@@

#3.mark which bivalents are above the threshold

@@

#rec group
Long.biv_mouse_table$Rec.group <- ifelse(grepl("PWD", Long.biv_mouse_table$category), 1, 
                            ifelse(grepl("MSM", Long.biv_mouse_table$category), 1,
                             ifelse(grepl("SKIVE", Long.biv_mouse_table$category), 1, 0)) )
